Approximate Code: A Cost-Effective Erasure Code for Video Applications in Cloud Storage Systems

### 2019-04-01 ApproximateCode.tex
Version 1.0.0

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{subfigure}

@@

%-------------------------ATTANTION-------------------------%
%                                                           %
% red words show the content that requires to be add        %
% blue words need to be perfected or changed                %
%                                                           %
%-----------------------------------------------------------%

@@

Therefore, we propose Approximate Codes for video data that significantly reduce storage overhead by reducing the parity of data that is not sensitive to errors. In the scenario shown in (Figure 1), the Approximate Codes are designed for systems composed of $n$ disks where $m$ disks are dedicated to coding and another $s$ sectors encoded for the first strip. This allows the data of the first stripe to tolerate any $m+s$ disks corruption, so we specifically store important segments of video data there. With an appropriate data distribution scheme, non-critical data segments will still retain $(n-2m-s)/(n-m)$ data when any $m+s$ disks are corrupted, which makes
recovery schemes such as interpolated or superpixel still effective. The Approximate Codes provide two recovery modes, full recovery and approximate recovery. The former applies to no more than $m$ disk corruptions and recovers all data, the latter applies to no more than $m+$s disks corruptions and retains important data.

\textcolor{red}
{Sixth paragraph:
Contribution of this paper, typically two or three contributions,
(1)	Propose a novel code Approximate Code
(2)	Give some mathematical proof to demonstrate the correctness of Approximate Code
(3)	Conduct several experiments to demonstrate the effectiveness of Approximate Code (no digitals here)}

\textcolor{red}
{Seventh paragraph:
organization of the paper}

@@

\textcolor{red}{Here we give some introduction to existing erasure codes
Specifically, we need to illustrate the existing erasure codes for video applications in detail.
Summarize the existing erasure codes in a table (assume Table 1), and illustrate them whether they satisfy the previous requirements in Section II.A}

@@

\textcolor{red}{Something about H.264\dots}

@@

\subsection{Design of Approximate Code}
In a system of $n$ disks, each disk can be divided into multiple sectors. We focus on the $r$ sectors of the same logical position of each device, and we treat these $r$ sectors as a \emph{chunk}. The $r \times n$ sectors of $n$ chunks constitute a stripe, as shown in Figure \ref{chunk-sector} . We also use the term symbol in coding theory to refer to sectors. Since each strip is independent of the entire system, we only consider a single strip.

@@

\textcolor{blue}{Although the choice of parameter $r$ is arbitrary, we recommend setting it to $r=s+h$ and the relevant instructions will be shown in ...}

Based on the above definition, our design has 4 configurable parameters $(n, m, r, s,t)$ that uniquely determine the construction of Approximate Code.
Figure \ref{apcode-72522} shows an example of Approximate Codes with $n = 7$, $m = 2$, $r=5$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the minor parity sectors with $p_{i,j}$.

We then define the set of sectors as follows:
\begin{itemize}
    \item $D_I=\{d_{i,j}|0\leqslant i < t, 0\leqslant j < h \}$ important data sector set.
    \item $D_M=\{d_{i,j}|t\leqslant i < r, 0\leqslant j < n-m \}$ minor data sector set.
    \item $Q=\{q_{i,j}|0\leqslant i < t, 0\leqslant j < s \}$ important parity sector set. 
    \item $G=\{p_{i,j}|0\leqslant i < r, 0\leqslant j < m \}$ global parity sector set.
\end{itemize}

\begin{figure}[h]
\centering
\subfigure[sector label and encoding process]{
    \includegraphics[width=0.32\textwidth]{photo/apcode-72522.PDF}
    \label{apcode-72522-a}
}
\subfigure[sector sets]{
    \includegraphics[width=0.13\textwidth]{photo/DDQG.PDF}
    \label{apcode-72522-b}
}
\caption{A sample of Approximate Codes $(7,2,5,2,2)$ with 7 chunks where 2 of them are parity chunks (orange set $G$) and each chunk has 5 sectors. In this example, there are 6 sectors (dark blue set $D_I$) for important data, 15 sectors (light blue set $D_M$) for minor data and 4 other sectors (red set $Q$) are designed for encoding important data.}
\label{apcode-72522}
\end{figure}

@@

\textcolor{red}{Coding matrix like below?}

@@

\subsubsection{ XOR-based Approximate Code}
\textcolor{red}{It is difficult to design XOR-based codes that m=2,s=1. Codes like EVENODD or STAR cannot be used to recover the important data when 3 disks fails. However, the desgin of m=1 is easy, because we only use horizontal parity blocks. }

\textcolor{red}{One other way to generate XOR parity sectors is to divide each sector into multiple smaller blocks and apply EVENODD or RAID6 on them. This might be too complex but its correctness is easy to proof.}

\subsection{\textcolor{red}{Proof of Correctness}}

\subsection{Intermediate Layer}\label{Intermediate Layer}
Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage module is needed to preprocess the data. In our design, the middle layer performs automatic data identification and data distribution, implementing \emph{I-Phase} in the encoding process and approximate recovery mode in the decoding process.

@@

\subsubsection{Data Distribution}
Fortunately, in an H.264 stream, each GOP begins with an I frame followed by a series of P and B frames. Therefore, we store data in units of GOPs. Our main purpose is to store I frames and other frames separately. For non-video data, we distribute it into multiple GOPs and treat it as a special part of the I frame. In the following description, we no longer consider such data especially and simply refer to them as I-frames.
Our data distribution algorithm is as follows:

\textcolor{red}{Need to draw an algorithm table from the following description}

1. Calculate the important data ratio of each GOP in a stripe, and remember that the highest one is $\omega_{max}$.

2. Adjust $t$ to find the important rate $\omega_{act}$ closest to $\omega_{max}$

3. Divide each GOP into two parts: $\omega_{act}$: $1-\omega_{act}$.

4. Store the former in $D_I$, the latter in $D_M$.

In this regard, the decoding process is as follows:

1. Read the entire strip and find the nmrst parameter of the strip record

2. Calculate $\omega_{act}$ based on parameters

3. Read the $I$ frame from $D_I$ until the next I frame is encountered

4. Calculate the length read in 3, multiply by $(1-\omega_{act})/\omega_{act}$ , and read this length in $D_M$.

5. Combine I frames with other frames.
The data distribution scheme is shown in the figure \ref{Data-distribution-v2}.

\textcolor{blue}{Some description about the figure...}

Our approach can be applied to a variety of other data types. In fact, encoded multimedia data mostly has the property of coexisting important data and non-essential data, such as PTC encoding used in image storage[][].

\begin{figure}[h]
\centering
\includegraphics[width=0.35\textwidth]{photo/Data-distribution-v2.PDF}
\caption{1}
\label{Data-distribution-v2}
\end{figure}

@@

\section{Evaluation}\label{evaluation}
\begin{table}[ht]
\begin{tabular}{|c|c|c|c|c|}
\hline
\begin{tabular}[c]{@{}c@{}}Code\\ Config\end{tabular} & \begin{tabular}[c]{@{}c@{}}Storage \\ Efficiency\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Imp)\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Minor)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Important \\ Rate\end{tabular} \\ \hline
(6,2,4,1,2) & 1.600 & 3 & 2 & 0.200 \\ \hline
(8,2,6,1,1) & 1.371 & 3 & 2 & 0.143 \\ \hline
(10,2,8,1,1) & 1.270 & 3 & 2 & 0.111 \\ \hline
(11,2,9,1,1) & 1.238 & 3 & 2 & 0.100 \\ \hline
(11,3,7,1,1) & 1.400 & 4 & 3 & 0.127 \\ \hline
(13,3,10,1,2) & 1.327 & 4 & 3 & 0.184 \\ \hline
(8,2,6,1,2) & 1.412 & 3 & 2 & 0.294 \\ \hline
(8,2,4,1,2) & 1.455 & 3 & 2 & 0.455 \\ \hline
(10,2,6,2,2) & 1.364 & 4 & 2 & 0.273 \\ \hline
(11,3,8,2,2) & 1.467 & 5 & 3 & 0.200 \\ \hline
\end{tabular}
\end{table}
\subsection{An Evaluation methodology}
\subsubsection{Erasure Codes in Our Comparisons}
\subsubsection{Platforms and Configurations}
\subsubsection{Metrics}
\subsubsection{Parameters and Assumption in Our Evaluation}

\subsection{Results}
\subsection{Analysis}
Illustrate why Approximate Code achieve high reliability with low cost
\section{Conclusion}

%
% The acknowledgments section is defined using the "acks" environment (and NOT an unnumbered section). This ensures
% the proper identification of the section in the article metadata, and the consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%
% The next two lines define the bibliography style to be used, and the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{ApproximateCode}

>>>>

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{subfigure}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{epsfig}
\renewcommand{\algorithmicrequire}{\textbf{Input:}} % Use Input in the format of Algorithm
\renewcommand{\algorithmicensure}{\textbf{Output:}} % Use Output in the format of Algorithm

@@

%-------------------------ATTANTION-------------------------%
%                                                           %
% orange words show the content that requires to be add     %
% blue words need to be perfected or changed                %
% gray words are the placeholder which is easy to fill      %
%                                                           %
%-----------------------------------------------------------%

@@

Therefore, we propose Approximate Codes for video data that significantly reduce storage overhead by reducing the parity of data that is not sensitive to errors. In the scenario shown in (Figure 1), the Approximate Codes are designed for systems composed of $n$ disks where $m$ disks are dedicated to coding and another $s$ sectors encoded for the first stripe. This allows the data of the first stripe to tolerate any $m+s$ disks corruption, so we specifically store important segments of video data there. With an appropriate data distribution scheme, non-critical data segments will still retain $(n-2m-s)/(n-m)$ data when any $m+s$ disks are corrupted, which makes
recovery schemes such as interpolated or superpixel still effective. The Approximate Codes provide two recovery modes, full recovery and approximate recovery. The former applies to no more than $m$ disk corruptions and recovers all data, the latter applies to no more than $m+$s disks corruptions and retains important data.

\textcolor{orange}
{Sixth paragraph:
Contribution of this paper, typically two or three contributions,
(1)	Propose a novel code Approximate Code
(2)	Give some mathematical proof to demonstrate the correctness of Approximate Code
(3)	Conduct several experiments to demonstrate the effectiveness of Approximate Code (no digitals here)}

\textcolor{orange}
{Seventh paragraph:
organization of the paper}

\textcolor{gray}{
    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text }

@@

\textcolor{orange}{Here we give some introduction to existing erasure codes
Specifically, we need to illustrate the existing erasure codes for video applications in detail.
Summarize the existing erasure codes in a table (assume Table 1), and illustrate them whether they satisfy the previous requirements in Section II.A}

\textcolor{gray}{
    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text }

@@

\textcolor{orange}{Something about H.264\dots}

\textcolor{gray}{
    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text 
    }

@@

\subsection{Design of Approximate Code}
In a system of $n$ disks, each disk can be divided into multiple sectors. We focus on the $r$ sectors of the same logical position of each device, and we treat these $r$ sectors as a \emph{chunk}. The $r \times n$ sectors of $n$ chunks constitute a stripe, as shown in Figure \ref{chunk-sector} . We also use the term symbol in coding theory to refer to sectors. Since each stripe is independent of the entire system, we only consider a single stripe.

@@

Based on the above definition, our design has 5 configurable parameters $(n, m, r, s,t)$ that uniquely determine the construction of Approximate Code.
Figure \ref{apcode-72522} shows an example of Approximate Codes with $n = 7$, $m = 2$, $r=5$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the minor parity sectors with $p_{i,j}$.

We then define the area of sectors as follows:
\begin{itemize}
    \item $D_I=\{d_{i,j}|0\leqslant i < t, 0\leqslant j < h \}$ important data sector area.
    \item $D_M=\{d_{i,j}|t\leqslant i < r, 0\leqslant j < n-m \}$ minor data sector area.
    \item $Q=\{q_{i,j}|0\leqslant i < t, 0\leqslant j < s \}$ important parity sector area. 
    \item $G=\{p_{i,j}|0\leqslant i < r, 0\leqslant j < m \}$ global parity sector area.
\end{itemize}

\begin{figure}[h]
\centering
\subfigure[sector label and encoding process]{
    \includegraphics[width=0.32\textwidth]{photo/apcode-72522.PDF}
    \label{apcode-72522-a}
}
\subfigure[sector sets]{
    \includegraphics[width=0.13\textwidth]{photo/DDQG.PDF}
    \label{apcode-72522-b}
}
\caption{A sample of Approximate Codes $(7,2,5,2,2)$ with 7 chunks where 2 of them are parity chunks (orange area $G$) and each chunk has 5 sectors. In this example, there are 6 sectors (dark blue area $D_I$) for important data, 15 sectors (light blue area $D_M$) for minor data and 4 other sectors (red area $Q$) are designed for encoding important data.}
\label{apcode-72522}
\end{figure}

@@

\textcolor{orange}{Coding matrix like below?}

@@

\subsubsection{ XOR-based Approximate Code}
\textcolor{orange}{It is difficult to design XOR-based codes that m=2,s=1. Codes like EVENODD or STAR cannot be used to recover the important data when 3 disks fails. However, the desgin of m=1 is easy, because we only use horizontal parity blocks. }

\textcolor{orange}{One other way to generate XOR parity sectors is to divide each sector into multiple smaller blocks and apply EVENODD or RAID6 on them. This might be too complex but its correctness is easy to proof.}

\textcolor{gray}{
    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text 
}

\subsection{\textcolor{orange}{Proof of Correctness}}
\textcolor{orange}{I am not quite clear what to write here, our proof of correctness is organized in encoding and decoding process}

\subsection{Intermediate Layer}\label{Intermediate Layer}
Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage module is necessary to preprocess the data. In our design, the middle layer performs automatic data identification and data distribution. It also implement \emph{I-Phase} in the encoding process and approximate recovery mode in the decoding process.

@@

\subsubsection{Data Distribution and Reorganization}
Fortunately, in an H.264 stream, each GOP begins with an I frame followed by a series of P and B frames. Therefore, we store data in units of GOPs. Our main purpose is to store I frames and other frames separately. For non-video data, we distribute it into multiple GOPs and treat it as a special part of the I frame. In the following description, we no longer consider such data especially and simply refer to them as I-frames.
We define $\omega$ as the the important data ratio, which is the size of I-frames divided by the entire GOP size. We also define $\omega_{act}=\frac{D_I}{D_I+D_M}=\frac{(n-m) \times t}{(n-m) \times r-s \times t}$ as the actual important rate the code can provide. Algorithm \ref{alg-data-dist} and \ref{alg-data-reor} shows the data distribution and reorganization methods.

\begin{algorithm}[htb] 
\caption{Data Distribution Algorithm} 
\label{alg-data-dist} 
\begin{algorithmic}[1]

\Require A stripe of video data.
\Ensure $D_I$ and $D_M$.

\State Divide video data into several GOPs;
\State Calculate $\omega$ of each GOP, and mark the highest one as $\omega_{max}$;
\State Adjust $t$ to find the closest $\omega_{act}$ to $\omega_{max}$;
\Repeat 
\State Divide each GOP into two parts: $\omega_{act}$ and $1-\omega_{act}$;
\State Store the former in $D_I$, the latter in $D_M$;
\Until All GOPs are classified;
\end{algorithmic} 
\end{algorithm}

\begin{algorithm}[htb] 
\caption{Data Reorganization Algorithm} 
\label{alg-data-reor} 
\begin{algorithmic}[1] 
\Require $D_I$ and $D_M$;
\Ensure A stripe of video data;
\State Find the parameter $(n,m,r,s,t)$ and calculate $\omega_{act}$.
\Repeat
\State Read an I frame from $D_I$ and record its length as $l$.
\State Read $l \times \frac{1-\omega_{act}}{\omega_{act}}$ in $D_M$ and combine two parts.
\Until All blocks are read.
\end{algorithmic} 
\end{algorithm}

The data distribution scheme is shown in the figure \ref{Data-distribution-v2}. We present $\omega_i$ as the $\omega$ of Data(i), and $\omega_{max} = \omega_2$.
For example, Data 3 is represnted by blue, and its key segment (10\%) and part of minor segment (10\%) are settled in $D_I$.
The main idea of our data distribution method is to guarantee that each GOP has the same proportion of storage in $D_I$ and $D_M$. This method improves flexibility because it is not necessary to maintain a map that marks the location of each GOP, which makes it is easy to add or delete data at any time. Meanwhile, the method is ideal for streaming video data generated in real time by applications such as monitoring.

\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth]{photo/Data-distribution-v2.pdf}
\caption{A sample of data distribution method, where the gray block in the upper right corner is the $Q$ area. Here for each data segment, $\omega_1=15\%$, $\omega_2=20\%$ and $\omega_3=10\%$, so the $\omega_{max}=20\%$.}
\label{Data-distribution-v2}
\end{figure}

In addition, our approach can be applied to a variety of other data types. In fact, encoded multimedia data mostly has the property of coexisting important data and non-essential data, such as PTC encoding used in image storage[][].

@@

\textcolor{gray}{
    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text 
}

\section{Evaluation}\label{evaluation}

\textcolor{gray}{
    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text 
}

\begin{table}[htbp]
\begin{tabular}{|c|c|c|c|c|}
\hline
\begin{tabular}[c]{@{}c@{}}Code\\ Config\end{tabular} & \begin{tabular}[c]{@{}c@{}}Storage \\ Efficiency\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Imp)\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Minor)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Important \\ Rate\end{tabular} \\ \hline
(6,2,4,1,2) & 1.600 & 3 & 2 & 0.200 \\ \hline
(8,2,6,1,1) & 1.371 & 3 & 2 & 0.143 \\ \hline
(10,2,8,1,1) & 1.270 & 3 & 2 & 0.111 \\ \hline
(11,2,9,1,1) & 1.238 & 3 & 2 & 0.100 \\ \hline
(11,3,7,1,1) & 1.400 & 4 & 3 & 0.127 \\ \hline
(13,3,10,1,2) & 1.327 & 4 & 3 & 0.184 \\ \hline
(8,2,6,1,2) & 1.412 & 3 & 2 & 0.294 \\ \hline
(8,2,4,1,2) & 1.455 & 3 & 2 & 0.455 \\ \hline
(10,2,6,2,2) & 1.364 & 4 & 2 & 0.273 \\ \hline
(11,3,8,2,2) & 1.467 & 5 & 3 & 0.200 \\ \hline
\end{tabular}
\end{table}

\subsection{An Evaluation methodology}

\subsubsection{Erasure Codes in Our Comparisons}
\textcolor{gray}{
    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
}

\subsubsection{Platforms and Configurations}
\textcolor{gray}{
    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
}

\subsubsection{Metrics}
\textcolor{gray}{
    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
}
\subsubsection{Parameters and Assumption in Our Evaluation}
\textcolor{gray}{
    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
}

\subsection{Results}
\textcolor{gray}{
    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
}

\subsection{Analysis}
\textcolor{orange}{Illustrate why Approximate Code achieve high reliability with low cost}
\textcolor{gray}{
    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
}
\section{Conclusion}

\textcolor{gray}{
    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
}

\begin{acks}

\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{ApproximateCode}
